---
title: "🏈 r/NFL Game Thread Summary"
subtitle: "made by u/CaptainScuttleBottom"
title-block-banner: www/turf-wide-dark.png
format: html
editor: visual
params:
  data: "/home/andrew/Documents/GitHub/sportsBs/data/nfl/2022-2023-playoffs/Game Thread: Dallas Cowboys (12-5) at San Francisco 49ers (13-4)-2023-01-25.rds"
  alt_color: FALSE
  yr: 2022
editor_options: 
  chunk_output_type: console
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
library(nflfastR)
library(tidyverse)
library(janitor)
library(ggthemes)
library(lubridate)
library(htmltools)
library(tidytext)
# library(wordcloud)
library(stringr)

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, 
                      out.width="85%", fig.align = "center")

team_info <- nflfastR::teams_colors_logos

# Read locally saved data ------------------------------------------------------
comments_ <- readr::read_rds(params$data)

thread_name <- comments_ |>
  distinct(title) |>
  pull(var = title)

# Cleaning ---------------------------------------------------------------------
comments_clean <- comments_ |>
  mutate(
    time = as_datetime(time_unix),
    ref_complaint = if_else(grepl(
      " REF | REFS|REFS |REFFING|REFEREE|OFFICIAL|OFFICIATING|OFFICIATED|REFFING|REFBALL|RIGGED|RIGGING|THE FIX|FUCKING FLAG|DAMN FLAG|TERRIBLE FLAG|BAD FLAG|BULLSHIT FLAG|AWFUL FLAG|BS FLAG|FUCKING CALL|DAMN CALL|TERRIBLE CALL|BAD CALL|BULLSHIT CALL|AWFUL CALL|BS CALL|FUCKING SPOT|DAMN SPOT|TERRIBLE SPOT|BAD SPOT|BULLSHIT SPOT|AWFUL SPOT|BS SPOT|HOSED|ROBBED",
      body, ignore.case = TRUE), 
      TRUE, FALSE),
    flair_clean = trimws(str_extract_all(flair, ":\\w+:")), 
    # bandwagon flairs are lumped in with non-bandwagon glairs
    flair_clean = str_remove_all(flair_clean, "c\\(|[:punct:]"),
    flair_clean = if_else(flair == "NULL", "no_flair", flair_clean)
  ) |>
  separate(col = flair_clean, sep = " ", into = c("flair_one", "flair_two")) |>
  separate(col = title, sep = " at ", into = c("away", "home"), remove = FALSE) |>
  mutate(
    away = str_remove(away, "Game Thread:"),
    away = trimws(str_replace_all(away, pattern = "[^a-zA-Z ]", "")),
    home = str_remove(home, " \\s*\\([^\\)]+\\)"),
    home = trimws(str_replace_all(home, pattern = "[^a-zA-Z ]", "")),
    # fix for 49ers
    home = if_else(home == "San Francisco ers", "San Francisco 49ers", home),
    away = if_else(away == "San Francisco ers", "San Francisco 49ers", away),
  ) |>
  rowwise() |>
  mutate(
    faction = case_when(
      # could speed this up if you could get them to match exactly. shouldn't be that hard
      grepl(flair_one, home, ignore.case = T) ~ "Home Team Fan",
      grepl(flair_one, away, ignore.case = T) ~ "Away Team Fan",
      TRUE ~ "Neutral / Both / Neither"
    ),
    flair_one = if_else(is.na(flair_one) | flair_one == "no_flair", "No Flair", flair_one)
  ) |>
  select(!flair) |>
  suppressWarnings()

# Game schedule data -----------------------------------------------------------
sched <- nflfastR::fast_scraper_schedules() |>
  filter(season == params$yr) |>
  left_join(team_info |>
              select("home_team_abbr" = team_abbr, "home_team_name" = team_name), 
            by = c("home_team" = "home_team_abbr")) |>
  left_join(team_info |>
              select("away_team_abbr" = team_abbr, "away_team_name" = team_name), 
            by = c("away_team" = "away_team_abbr")) |>
  select(!c(old_game_id, gsis, nfl_detail_id, pfr, pff, espn, away_rest, home_rest,
            div_game, away_qb_id, home_qb_id, stadium_id)) |>
  filter(home_team_name %in% comments_clean$home,
         away_team_name %in%comments_clean$away) 



# Final Dataset ----------------------------------------------------------------
comments <- comments_clean |>
  left_join(sched, by = c("home" = "home_team_name")) |>
  group_by(title) |>
  mutate(start_date = ymd_hm(paste(gameday, gametime)) + hours(5),
         end_date = start_date + hours(4) + minutes(30))

# QOL dataframes ---
home_team_name <- comments |> distinct(home) |> pull(var = home)
home_team_logo <- team_info[which(team_info$team_name == home_team_name), ]$team_logo_espn

if(params$alt_color){
  home_team_color <- team_info[which(team_info$team_name == home_team_name), ]$team_color2
} else {
  home_team_color <- team_info[which(team_info$team_name == home_team_name), ]$team_color
}

away_team_name <- comments |> distinct(away) |> pull(var = away)
away_team_logo <- team_info[which(team_info$team_name == away_team_name), ]$team_logo_espn

away_team_color <- team_info[which(team_info$team_name == away_team_name), ]$team_color
# away_team_color_alt <- team_info[which(team_info$school == away_team_name), ]$alt_color
 
top_flair_summary <- comments |> 
  count(flair_one) |> 
  ungroup() |>
  slice_max(order_by = n, n = 1)

top_flair_logo <- team_info[which(team_info$team_name == top_flair_summary |> 
                                    pull(var = flair_one)), ]$team_logo_espn
if(top_flair_summary |> pull(var = flair_one) == "No Flair"){
  top_flair_logo <- "./www/clown.png"
}

total_ref_complaints <- comments |> 
  filter(ref_complaint) |> 
  nrow() 
  
percent_ref_complaints <- (total_ref_complaints / nrow(comments)) |>
  round(2)

top_ref_complainer_data <- comments |>
  filter(ref_complaint) |>
  group_by(flair_one) |>
  summarize(
    n_complaints = n()
  ) |>
  slice_max(order_by = n_complaints, n = 1)

top_ref_complainer <- top_ref_complainer_data |> pull(var = flair_one)
if(length(top_ref_complainer) > 1){
  top_ref_complainer <- paste(top_ref_complainer, collapse = "/")
}

top_ref_complainer_logo <- team_info[which(team_info$team_name == top_ref_complainer), ]$team_logo_espn
if(top_ref_complainer == "No Flair"){
  top_ref_complainer_logo <- "./www/clown.png"
}
if(is_empty(top_ref_complainer_logo)){
  top_ref_complainer_logo <- "./www/cfb-imp-map-logo-dark.png"
}

# Ref complaint index
ref_complaint_rating <- case_when(
  percent_ref_complaints < 0.025 ~ "Clear",
  percent_ref_complaints >= 0.025 & percent_ref_complaints < 0.05 ~ "Mild",
  percent_ref_complaints >= 0.05 & percent_ref_complaints < 0.075 ~ "Moderate",
  percent_ref_complaints >= 0.075 & percent_ref_complaints < .1 ~ "High",
  percent_ref_complaints >= .1 & percent_ref_complaints < .125 ~ "Extreme",
  percent_ref_complaints >= .125 ~ "Oh Shit!",
)

```

```{css}
h1 {
  margin-top: -20px;
}
```

# `r str_remove_all(thread_name, "\\[Game Thread\\]|.csv") |> trimws()`

------------------------------------------------------------------------

## 📈 Summary Statistics

<!-- -   **Game Start Time:** `r comments |> distinct(start_date) |> pull(var = start_date)` (UTC) -->

-   **Total Comments at time of data collection:** `r comments |> nrow() |> format(big.mark = ",")`



-   **Most Common Primary Flair:** `r top_flair_summary |> pull(var = flair_one)` ![](`r top_flair_logo`){style="height: 25px; width: 25px;"} (`r top_flair_summary |> pull(var = n) |> format(big.mark = ",")` comments)

-   **Total Comments from:**

    -   **Neutral / No Flairs:** `r comments |> filter(faction == "Neutral / Both / Neither") |> nrow() |> format(big.mark = ",")` (`r ( 100 * comments |> filter(faction == "Neutral / Both / Neither") |> nrow() / nrow(comments) ) |> round(2)`%)

    -   **`r home_team_name` flairs:** 
    ![](`r home_team_logo`){style="height: 25px; width: 25px;"} 
    `r comments |> filter(faction == "Home Team Fan") |> nrow() |> format(big.mark = ",")` 
    (`r ( 100 * comments |> filter(faction == "Home Team Fan") |> nrow() / nrow(comments) ) |> round(2)`%)

    -   **`r away_team_name` flairs:** 
    ![](`r away_team_logo`){style="height: 25px; width: 25px;"} 
    `r comments |> filter(faction == "Away Team Fan") |> nrow() |> format(big.mark = ",")` 
    (`r ( 100 * comments |> filter(faction == "Away Team Fan") |> nrow() / nrow(comments) ) |> round(2)`%)

## ⌚ Thread Timeline

```{r thread_timeline}
thread_timeline_data <- comments |> 
  filter(home == home_team_name) |>
  count(
    min = floor_date(time, "10 minutes"),
    title,
    faction,
    start_date, end_date
    ) |> 
  filter(min > start_date - minutes(30),
         min < end_date)

thread_timeline_data |>
  ggplot(aes(x = min, y = n, 
             fill = faction, 
             # color = faction
             )) +
  geom_col() +
    expand_limits(x = c(thread_timeline_data$start_date - minutes(30),
                        thread_timeline_data$end_date)) +
  scale_y_continuous(labels = scales::comma) +
  labs(title = paste0(str_remove_all(thread_name, "\\[Game Thread\\]|.csv"), "\n Game Thread Timeline"),
       subtitle = "Total comments posted per 10 minute interval, by commenter's primary flair",
       x = "Comment time (10 minute chunks)",
       y = "Total comments",
       fill = "Commenter Faction") +
  theme_fivethirtyeight() +
  scale_fill_manual(labels = c(away_team_name, home_team_name, "Neutral / No Flair"),
                    values = c(away_team_color, home_team_color, "#D3D3D3")) +
  # scale_color_manual(breaks = c("Away Team Fan", "Home Team Man", "Neutral / Both / Neither"),
  #                    values = c(away_team_color_alt, home_team_color_alt, "#D3D3D3")) +
  guides(color = "none") +
  theme(legend.direction = "horizontal",
        legend.position = "bottom",
        axis.text.y = element_text(size = 13),
        axis.title = element_text(),
        plot.title.position = "plot",
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))

# comments |>
#   filter(faction != "Neutral / Both / Neither") |>
#   count(time = floor_date(time, "10 minutes"), faction) |>
#   ggplot(aes(x = time, y = n, color = faction)) +
#   geom_line(size = 2) +
#   theme_fivethirtyeight() +
#   scale_color_manual(labels = c(away_team_name, home_team_name, "Neutral / No Flair"),
#                    values = c(away_team_color, home_team_color, "#D3D3D3")) +
#   labs(title = "r/CFB game thread",
#        subtitle = "Comments per 10 minutes",
#        x = "Time",
#        y = "Comments / 10 minutes")

```

## 🤡 Referee Complaint Analysis

-   **Total Complaints:** `r total_ref_complaints |> format(big.mark = ",")` (`r 100 * percent_ref_complaints`% of all comments) -- RATING: \[`r ref_complaint_rating`\]

-   **Top Complainers:** `r top_ref_complainer` ![](`r top_ref_complainer_logo`){style="height: 25px; width: 25px;"} (`r (100 * top_ref_complainer_data |> pull(var = n_complaints) / comments |> filter(ref_complaint) |> nrow()) |> round(2)`% of all complaints and `r (100 * top_ref_complainer_data |> pull(var = n_complaints) / nrow(comments)) |> round(2)`% of all comments)

```{r ref_complaint_timeline}
ref_timeline_data <- comments |> 
  filter(home == home_team_name,
         ref_complaint) |>
  count(
    min = floor_date(time, "10 minutes"),
    title,
    faction,
    start_date, end_date
    ) |> 
  filter(min > start_date - minutes(30),
         min < end_date)

ref_timeline_data |>
ggplot(aes(x = min, y = n, 
             fill = faction, 
             # color = faction
             )) +
  geom_col() +
  scale_y_continuous(labels = scales::comma) +
  expand_limits(x = c(ref_timeline_data$start_date - minutes(30), 
                      ref_timeline_data$end_date)) +
  labs(title = paste0(str_remove_all(thread_name, "\\[Game Thread\\]|.csv"), "\nRef Complaint Timeline"),
       subtitle = "Total ref complaints posted per 10 minute interval, by commenter's primary flair",
       x = "Comment time (10 minute chunks)",
       y = "Total comments\ncomplaining about refs",
       fill = "Commenter Faction") +
  theme_fivethirtyeight() +
  scale_fill_manual(labels = c(away_team_name, home_team_name, "Neutral / No Flair"),
                    values = c(away_team_color, home_team_color, "#D3D3D3")) +
  # scale_color_manual(breaks = c("Away Team Fan", "Home Team Man", "Neutral / Both / Neither"),
  #                    values = c(away_team_color_alt, home_team_color_alt, "#D3D3D3")) +
  guides(color = "none") +
  theme(legend.direction = "horizontal",
        legend.position = "bottom",
        axis.text.y = element_text(size = 13),
        axis.title = element_text(),
        plot.title.position = "plot",
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))
```

## 🗣 Most Common Words Analysis

```{r, fig.height=6, out.width='90%'}

top_words <- comments |>
  mutate(text = body,
         text = str_remove_all(text, "&amp;|&lt;|&gt;"),
         text = str_remove_all(text, "\\s?(f|ht)(tp)(s?)(://)([^\\.]*)[\\.|/](\\S*)"),
         text = str_remove_all(text, "[^\x01-\x7F]")) |>
  group_by(faction) |>
  unnest_tokens(word, text, token = "words") |>
  filter(!word %in% stop_words$word,
         !word %in% str_remove_all(stop_words$word, "'"),
         str_detect(word, "[a-z]"),
         !str_detect(word, "^#"),
         !str_detect(word, "@\\S+")) |>
  count(word, sort = TRUE) |>
  filter(
    word != "game",
    # word != tolower(home_team_name),
    # word != tolower(away_team_name)
  ) |>
  slice_max(order_by = n, n = 10,
            with_ties = FALSE) |>
  mutate(reorder_word = reorder_within(word, n, faction))

top_words |>
  filter(faction != "Neutral / Both / Neither") |>
  ggplot(aes(x = reorder_word,
             y = n,
             fill = faction)) +
  geom_col(position = "dodge") +
  geom_text(aes(label = word),
            color = "white",
            size = 6,
            hjust = 1,
            fontface = "bold"
            ) +
  coord_flip() +
  scale_x_reordered() +
  labs(title = "Top 10 Most Used Words",
       subtitle = "by commenter faction",
       x = "", y = "") +
  facet_wrap(~faction,
             nrow = 1,
             scales = "free") +
  theme_fivethirtyeight() +
  guides(fill = "none") +
  scale_fill_manual(labels = c(away_team_name, home_team_name, "Neutral / No Flair"),
                    values = c(away_team_color, home_team_color, "#D3D3D3")) +
  theme(legend.direction = "horizontal",
        legend.position = "bottom",
        # axis.text.y = element_text(size = 13),
        # axis.text.x. = element_blank(),
        axis.text.y = element_blank(), 
        axis.title = element_text(),
        plot.title.position = "plot",
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))
  
```
