---
title: "🏈 r/CFB Game Thread Summary"
subtitle: "made by u/CaptainScuttleBottom"
title-block-banner: www/turf-wide-dark.png
format: html
editor: visual
params:
  data: "/home/andrew/Documents/GitHub/sportsBs/data/reddit-comment-data/cfb/2023/week-3/[Game Thread] Colorado State @ Colorado (10:00 PM ET)-2023-09-17.rds"
  alt_color: FALSE
  yr: 2023
editor_options: 
  chunk_output_type: console
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
library(cfbfastR)
library(tidyverse)
library(janitor)
library(ggthemes)
library(lubridate)
library(htmltools)
library(tidytext)
# library(wordcloud)
library(stringr)
devtools::load_all(".")

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, 
                      out.width="85%", fig.align = "center")

team_info <- cfbfastR::cfbd_team_info() |>
  dplyr::mutate(
    school = case_when(
      school == "East Carolina" ~ "ECU",
      TRUE ~ school
    )
  )

# Read locally saved data ------------------------------------------------------
comments_ <- readr::read_rds(params$data)

thread_name <- comments_ |>
  distinct(title) |>
  pull(var = title)

# Cleaning ---------------------------------------------------------------------
comments_clean <- comments_ |>
  sportsBs::clean_rcfb_comments() |>
  mutate(
    faction = case_when(
      flair_one == home ~ "Home Team Fan",
      flair_one == away ~ "Away Team Fan",
      TRUE ~ "Neutral / Both / Neither"
    )
  )


  # mutate(
  #   time = as_datetime(time_unix, tz = "America/Chicago"),
  #   ref_complaint = if_else(grepl(
  #     " REF | REFS|REFS |REFFING|REFEREE|OFFICIAL|OFFICIATING|OFFICIATED|REFFING|REFBALL|RIGGED|RIGGING|THE FIX|FUCKING FLAG|DAMN FLAG|TERRIBLE FLAG|BAD FLAG|BULLSHIT FLAG|AWFUL FLAG|BS FLAG|FUCKING CALL|DAMN CALL|TERRIBLE CALL|BAD CALL|BULLSHIT CALL|AWFUL CALL|BS CALL|FUCKING SPOT|DAMN SPOT|TERRIBLE SPOT|BAD SPOT|BULLSHIT SPOT|AWFUL SPOT|BS SPOT|HOSED|ROBBED",
  #     body, ignore.case = TRUE),
  #     TRUE, FALSE),
  #   flair = trimws(str_remove(flair, "\\:[^()]*\\:")),
  #   flair = if_else(flair == "NULL", "No Flair", flair)
  # ) |>
  # separate(col = flair, sep = " • ", into = c("flair_one", "flair_two")) |>
  # separate(col = title, sep = " @ | vs. ", into = c("away", "home"), remove = FALSE) |>
  # mutate(
  #   away = str_remove(away, "\\[Game Thread]"),
  #   away = trimws(str_replace_all(away, pattern = "[^a-zA-Z ]", "")),
  #   home = str_remove(home, " \\s*\\([^\\)]+\\)"),
  #   home = trimws(str_replace_all(home, pattern = "[^a-zA-Z ]", "")),
  # ) |>
  # # FLAIR FIXES
  # mutate(
  #   home = case_when(
  #     home == "Texas AM" ~ "Texas A&M",
  #     TRUE ~ home
  #   )
  # ) |>
  # group_by(title) |>
  # mutate(
  #   faction = case_when(
  #     flair_one == home ~ "Home Team Fan",
  #     flair_one == away ~ "Away Team Fan",
  #     TRUE ~ "Neutral / Both / Neither"
  #   ),
  #   flair_one = if_else(is.na(flair_one), "No Flair", flair_one)
  # ) |>
  # ungroup()

# Game schedule data -----------------------------------------------------------
sched <- cfbfastR::espn_cfb_schedule(year = params$yr) |>
  select(game_date, home_team_location, away_team_location, start_date) |>
  mutate(
    home_team_location = case_when(
      home_team_location == "South Florida" ~ "USF",
      TRUE ~ home_team_location
    )
  ) |>
  filter(home_team_location %in% comments_clean$home | home_team_location %in% comments_clean$away,
         away_team_location %in% comments_clean$away | away_team_location %in% comments_clean$home)

# Final Datasets ----------------------------------------------------------------
comments <- comments_clean |>
  # left_join(sched, by = c("home" = "home_team_location")) |>
  mutate(
    start_date = sched$start_date[1],
    start_date = parse_datetime(start_date),
    end_date = start_date + hours(4) + minutes(30)
    ) 

unique_users <- comments |>
  group_by(author) |>
  summarize(
    n_comments = n(),
    n_comments_formatted = format(n_comments, big.mark = ","),
    avg_score = mean(score, na.rm = T),
    n_downvoted = sum(score < 1, na.rm = T),
    p_downvoted = n_downvoted / n_comments,
    n_unique_threads = n_distinct(title_clean, na.rm = T),
    all_primary_flairs = paste0(unique(flair_one), collapse = ", "),
    all_secondary_flairs = paste0(unique(flair_two), collapse = ", "),
    flair_list = list(unique(flair_one)),
    # TODO: replace this with something where instead of first() it's explicitly
    # looping through and pulling out the first one that's not "Unflaired"
    counted_flair = purrr::map_chr(flair_list, first),
    flaired_up = if_else(str_detect(all_primary_flairs, ","), TRUE, FALSE),
    n_swears = sum(swear, na.rm = T),
    p_swears = sum(n_swears) / n_comments,
    n_ref_comps = sum(ref_complaint, na.rm = T),
    p_ref_comps = sum(n_ref_comps) / n_comments,
    n_ads = sum(ad_complaint, na.rm = T),
    p_ads = sum(n_ads) / n_comments
  )

summary_flair <- unique_users |>
  group_by(counted_flair) |>
  summarize(
    n_unique_users = n(),
    n_total_comments = sum(n_comments, na.rm = T),
    avg_comments_per_user = n_total_comments / n_unique_users,
    avg_avg_score = mean(avg_score, na.rm = T),
    p_swears = sum(n_swears) / n_total_comments,
    p_ref_comps = sum(n_ref_comps) / n_total_comments,
    # p_ads = sum(n_ads) / n_total_comments
  ) 

# QOL dataframes ---
home_team_name <- comments |> distinct(home) |> pull(var = home)
home_team_logo <- team_info[which(team_info$school == home_team_name), ]$logo

if(params$alt_color){
  home_team_color <- team_info[which(team_info$school == home_team_name), ]$alt_color
} else {
  home_team_color <- team_info[which(team_info$school == home_team_name), ]$color
}

away_team_name <- comments |> distinct(away) |> pull(var = away)
away_team_logo <- team_info[which(team_info$school == away_team_name), ]$logo

away_team_color <- team_info[which(team_info$school == away_team_name), ]$color
# away_team_color_alt <- team_info[which(team_info$school == away_team_name), ]$alt_color
 
top_flair_summary <- comments |> count(flair_one) |> slice_max(order_by = n, n = 1)
top_flair_logo <- team_info[which(team_info$school == top_flair_summary |> pull(var = flair_one)), ]$logo
if(top_flair_summary |> pull(var = flair_one) == "Unflaired"){
  top_flair_logo <- "./www/clown.png"
}

total_ref_complaints <- comments |> 
  filter(ref_complaint) |> 
  nrow() 
  
percent_ref_complaints <- (total_ref_complaints / nrow(comments)) |>
  round(2)

top_ref_complainer_data <- comments |>
  filter(ref_complaint) |>
  group_by(flair_one) |>
  summarize(
    n_complaints = n()
  ) |>
  slice_max(order_by = n_complaints, n = 1)

top_ref_complainer <- top_ref_complainer_data |> pull(var = flair_one)
if(length(top_ref_complainer) > 1){
  top_ref_complainer <- paste(top_ref_complainer, collapse = "/")
}

top_ref_complainer_logo <- team_info[which(team_info$school == top_ref_complainer), ]$logo
if(top_ref_complainer == "Unflaired"){
  top_ref_complainer_logo <- "./www/clown.png"
}
if(is_empty(top_ref_complainer_logo)){
  top_ref_complainer_logo <- "./www/cfb-imp-map-logo-dark.png"
}

# Ref complaint index
ref_complaint_rating <- case_when(
  percent_ref_complaints < 0.025 ~ "Clear",
  percent_ref_complaints >= 0.025 & percent_ref_complaints < 0.05 ~ "Mild",
  percent_ref_complaints >= 0.05 & percent_ref_complaints < 0.075 ~ "Moderate",
  percent_ref_complaints >= 0.075 & percent_ref_complaints < .1 ~ "High",
  percent_ref_complaints >= .1 & percent_ref_complaints < .125 ~ "Extreme",
  percent_ref_complaints >= .125 ~ "Oh Shit!",
)

```

```{css}
h1 {
  margin-top: -20px;
}
```

# `r str_remove_all(thread_name, "\\[Game Thread\\]|.csv") |> trimws()`

------------------------------------------------------------------------

## 📈 Summary Statistics

<!-- -   **Game Start Time:** `r comments |> distinct(start_date) |> pull(var = start_date)` (UTC) -->

-   **Total Comments at time of data collection:** `r comments |> nrow() |> format(big.mark = ",")`



-   **Most Common Primary Flair:** `r top_flair_summary |> pull(var = flair_one)` ![](`r top_flair_logo`){style="height: 25px; width: 25px;"} (`r top_flair_summary |> pull(var = n) |> format(big.mark = ",")` comments)

-   **Total Comments from:**

    -   **Neutral / No Flairs:** `r comments |> filter(faction == "Neutral / Both / Neither") |> nrow() |> format(big.mark = ",")` (`r ( 100 * comments |> filter(faction == "Neutral / Both / Neither") |> nrow() / nrow(comments) ) |> round(2)`%)

    -   **`r home_team_name` flairs:** 
    ![](`r home_team_logo`){style="height: 25px; width: 25px;"} 
    `r comments |> filter(faction == "Home Team Fan") |> nrow() |> format(big.mark = ",")` 
    (`r ( 100 * comments |> filter(faction == "Home Team Fan") |> nrow() / nrow(comments) ) |> round(2)`%)

    -   **`r away_team_name` flairs:** 
    ![](`r away_team_logo`){style="height: 25px; width: 25px;"} 
    `r comments |> filter(faction == "Away Team Fan") |> nrow() |> format(big.mark = ",")` 
    (`r ( 100 * comments |> filter(faction == "Away Team Fan") |> nrow() / nrow(comments) ) |> round(2)`%)

## ⌚ Thread Timeline

```{r thread_timeline}
thread_timeline_data <- comments |> 
  filter(home == home_team_name) |>
  count(
    min = floor_date(time, "10 minutes"),
    title,
    faction,
    start_date, end_date
    ) |> 
  filter(min > start_date - minutes(30),
         min < end_date)

thread_timeline_data |>
  ggplot(aes(x = min, y = n, 
             fill = faction, 
             # color = faction
             )) +
  geom_col() +
    expand_limits(x = c(thread_timeline_data$start_date - minutes(30),
                        thread_timeline_data$end_date)) +
  scale_y_continuous(labels = scales::comma) +
  labs(title = paste0(str_remove_all(thread_name, "\\[Game Thread\\]|.csv"), "\n Game Thread Timeline"),
       subtitle = "Total comments posted per 10 minute interval, by commenter's primary flair",
       x = "Comment time (10 minute chunks, CST)",
       y = "Total comments",
       fill = "Commenter Faction") +
  theme_fivethirtyeight() +
  scale_fill_manual(labels = c(away_team_name, home_team_name, "Neutral / No Flair"),
                    values = c(away_team_color, home_team_color, "#D3D3D3")) +
  # scale_color_manual(breaks = c("Away Team Fan", "Home Team Man", "Neutral / Both / Neither"),
  #                    values = c(away_team_color_alt, home_team_color_alt, "#D3D3D3")) +
  guides(color = "none") +
  theme(legend.direction = "horizontal",
        legend.position = "bottom",
        axis.text.y = element_text(size = 13),
        axis.title = element_text(),
        plot.title.position = "plot",
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))

```

```{r team_thread_timeline, fig.height=1.5}
comments |>
  filter(faction != "Neutral / Both / Neither") |>
  count(
    faction,
    start_date,
    end_date,
    min = floor_date(time, "10 minutes")
  ) |>
  filter(min > start_date - minutes(30),
         min < end_date + minutes(30)) |>
  ggplot(aes(x = min, 
             y = n,
             color = faction)) +
  geom_line(linewidth = 1.5) +
  theme_fivethirtyeight() +
  scale_color_manual(labels = c(away_team_name, home_team_name),
                     values = c(away_team_color, home_team_color)) +
  # scale_color_manual(breaks = c("Away Team Fan", "Home Team Man", "Neutral / Both / Neither"),
  #                    values = c(away_team_color_alt, home_team_color_alt, "#D3D3D3")) +
  guides(color = "none")

# comments |>
#   filter(faction != "Neutral / Both / Neither") |>
#   count(time = floor_date(time, "10 minutes"), faction) |>
#   ggplot(aes(x = time, y = n, color = faction)) +
#   geom_line(size = 2) +
#   theme_fivethirtyeight() +
#   scale_color_manual(labels = c(away_team_name, home_team_name, "Neutral / No Flair"),
#                    values = c(away_team_color, home_team_color, "#D3D3D3")) +
#   labs(title = "r/CFB game thread",
#        subtitle = "Comments per 10 minutes",
#        x = "Time",
#        y = "Comments / 10 minutes")

# More comment analysis (holy shit this is so messy jeez):

top_swear_flair <- summary_flair |> 
  filter(n_total_comments > 0.03 * nrow(comments)) |> 
  slice_max(order_by = p_swears, n = 1)

top_neutral <- summary_flair |>
  filter(counted_flair != away_team_name,
         counted_flair != home_team_name,
         counted_flair != "Unflaired") |>
  slice_max(order_by = n_total_comments, n = 5) |>
  mutate(counted_flair = paste0(counted_flair, " (", format(n_total_comments, big.mark = ","), ")")) |>
  pull(var = counted_flair) |>
  paste(collapse = ", ")

unflaired_n <- summary_flair |>
  filter(counted_flair == "Unflaired") |>
  mutate(
    n_total_comments = paste0(format(n_total_comments, big.mark = ","), 
                              " (", round(100 * n_total_comments / nrow(comments), 2), "% of total)")
  ) |>
  pull(var = n_total_comments) 

```

## ⌨️ Comment Analysis

-   🤡  **Total Ref Complaints:** `r total_ref_complaints |> format(big.mark = ",")` (`r 100 * percent_ref_complaints`% of all comments) -- RATING: \[`r ref_complaint_rating`\]

-   🗯️  **Top Ref Complainers:** `r top_ref_complainer` ![](`r top_ref_complainer_logo`){style="height: 25px; width: 25px;"} (`r (100 * top_ref_complainer_data |> pull(var = n_complaints) / comments |> filter(ref_complaint) |> nrow()) |> round(2)`% of all complaints and `r (100 * top_ref_complainer_data |> pull(var = n_complaints) / nrow(comments)) |> round(2)`% of all comments)

-   🤬  **Highest Swear %:** Of flairs making up at least 3% of the comments in the thread, **`r top_swear_flair$counted_flair[1]` flairs** had the highest swear rate, with `r 100 * top_swear_flair$p_swears[1] |> round(4)`% of their comments containing a foul-mouthed remark.

-   👀  **Top Five Most Common Neutral Flairs:** `r top_neutral`

-   🤮  **Total Unflaired Comments:** `r unflaired_n`

```{r ref_complaint_timeline}
ref_timeline_data <- comments |> 
  filter(home == home_team_name,
         ref_complaint) |>
  count(
    min = floor_date(time, "10 minutes"),
    title,
    faction,
    start_date, end_date
    ) |> 
  filter(min > start_date - minutes(30),
         min < end_date)

ref_timeline_data |>
ggplot(aes(x = min, y = n, 
             fill = faction, 
             # color = faction
             )) +
  geom_col() +
  scale_y_continuous(labels = scales::comma) +
  expand_limits(x = c(ref_timeline_data$start_date - minutes(30), 
                      ref_timeline_data$end_date)) +
  labs(title = paste0(str_remove_all(thread_name, "\\[Game Thread\\]|.csv"), "\nRef Complaint Timeline"),
       subtitle = "Total ref complaints posted per 10 minute interval, by commenter's primary flair",
       x = "Comment time (10 minute chunks, CST)",
       y = "Total comments\ncomplaining about refs",
       fill = "Commenter Faction") +
  theme_fivethirtyeight() +
  scale_fill_manual(labels = c(away_team_name, home_team_name, "Neutral / No Flair"),
                    values = c(away_team_color, home_team_color, "#D3D3D3")) +
  # scale_color_manual(breaks = c("Away Team Fan", "Home Team Man", "Neutral / Both / Neither"),
  #                    values = c(away_team_color_alt, home_team_color_alt, "#D3D3D3")) +
  guides(color = "none") +
  theme(legend.direction = "horizontal",
        legend.position = "bottom",
        axis.text.y = element_text(size = 13),
        axis.title = element_text(),
        plot.title.position = "plot",
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))
```

## 🗣 Most Common Words

```{r, fig.height=6, out.width='90%'}

home_abbr <- tolower(gsub("(?<=[A-Z])[^A-Z]+", "", home_team_name, perl = TRUE))
home_abbr2 <- paste0(home_abbr, "u")
home_abbr3 <- paste0("u", home_abbr)
away_abbr <- tolower(gsub("(?<=[A-Z])[^A-Z]+", "", away_team_name, perl = TRUE))
away_abbr2 <- paste0(away_abbr, "u")
away_abbr3 <- paste0("u", away_abbr)

top_words <- comments |>
  mutate(text = body,
         text = str_remove_all(text, "&amp;|&lt;|&gt;"),
         text = str_remove_all(text, "\\s?(f|ht)(tp)(s?)(://)([^\\.]*)[\\.|/](\\S*)"),
         text = str_remove_all(text, "[^\x01-\x7F]")) |>
  unnest_tokens(word, text, token = "words") |>
  filter(!word %in% stop_words$word,
         !word %in% str_remove_all(stop_words$word, "'"),
         str_detect(word, "[a-z]"),
         !str_detect(word, "^#"),
         !str_detect(word, "@\\S+")) |>
  group_by(faction) |>
  count(word, sort = TRUE) |>
  filter(
    word != "game", word != "lol",
    word != tolower(home_team_name),
    word != tolower(away_team_name),
    word != home_abbr & word != home_abbr2 & word != home_abbr3,
    word != away_abbr & word != away_abbr2 & word != away_abbr3
  ) |>
  slice_max(order_by = n, n = 10,
            with_ties = FALSE) |>
  mutate(reorder_word = reorder_within(word, n, faction))

top_words |>
  # filter(faction != "Neutral / Both / Neither") |>
  ggplot(aes(x = reorder_word,
             y = n,
             fill = faction)) +
  geom_col(position = "dodge") +
  geom_text(aes(label = word),
            color = "white",
            size = 6,
            hjust = 1,
            fontface = "bold"
            ) +
  coord_flip() +
  scale_x_reordered() +
  labs(title = "Top 10 Most Used Words",
       subtitle = "by commenter faction",
       x = "", y = "") +
  facet_wrap(~faction,
             nrow = 1,
             scales = "free") +
  theme_fivethirtyeight() +
  guides(fill = "none") +
  scale_fill_manual(labels = c(away_team_name, home_team_name, "Neutral / No Flair"),
                    values = c(away_team_color, home_team_color, "#D3D3D3")) +
  theme(legend.direction = "horizontal",
        legend.position = "bottom",
        # axis.text.y = element_text(size = 13),
        # axis.text.x. = element_blank(),
        axis.text.y = element_blank(), 
        axis.title = element_text(),
        plot.title.position = "plot",
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))
  
```
